Process_OlisJazEmData

### 2024-05-12 Code/Process_OlisJazEmData.Rmd
Fixed duplication of data

# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257
```{r join whole cell absorbance with MC emission data}

@@

OlisJazMetaData <- OlisJazMetaData %>% 
  group_by(SampleID, E_days) %>%
 mutate(AbsNorm440 = Absorbance / MaxAbs_Blue,
        AbsNorm675 = Absorbance / MaxAbs_Red) %>% 
  ungroup()

>>>>

# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257 Multicultivators
```{r join whole cell absorbance with MC emission data}

@@

OlisJazMetaData <- OlisJazMetaData %>% 
  filter(E_days != 1) %>%  # remove absorbance spectra data collected during lag phase
  group_by(SampleID, E_days) %>%
 mutate(AbsNorm440 = Absorbance / MaxAbs_Blue,
        AbsNorm675 = Absorbance / MaxAbs_Red) %>% 
  ungroup()
